On the discovery of K-enhanced and possibly Mg-depleted stars throughout the Milky Way\footnote{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}

### 2018-07-09 article/Referee responses 2.txt

Referee responses 2

Comments to the Author
I thank the authors to improve the manuscript that now it is 
ready to be recommended for the publication. 
I repeat my previous comment, the lack of a (small) sample of stars 
observed with LAMOST and with normal [K/Fe] weakens the result, 
because the suspect of possible systematics remains and the 
comparison with APOGEE data is not homogeneous. 
My suggestion would be to include a sample of about 50/100 LAMOST targets 
with metallicity similar to that of the K-rich stars but 
with not enhanced K abundances, in order to quantitatively estimate 
the amount of K enrichment of these stars. 
This is my own opinion to enforce the result but I understand that this 
task is an additional and probably time-consuming effort.
The authors are free to follow or not this suggestion.

- Regrettably, undertaking the abundance estimation for LAMOST targets
- is a non-trivial endeavour, and while taking a smaller sample makes
- the problem more tractable, the reduced sample size diminishes the
- significance of the result. For this reason, we have opted to not
- include an additional sample of LAMOST stars, and have instead started
- a high-resolution spectroscopic campaign to measure detailed chemical
- abundances for a large number of normal and Mg-K stars. The detailed
- chemical abundances to be measured in that program will undoubtedly
- shed light on the origin of the Mg-K anomaly.

@@

3) Please provide the coordinates of the targets in Table A2 
with a more significant number of digits.

- Table A2 Right Ascension and Declination coordinates are now provided to 4 decimal points (units: degrees) in Table A2.

4) Please provide the statistical significance of the 
[K/Fe]-[Fe/H] anticorrelation.

- The linear regression using the LAMOST abundances is now included in Figure 7,
- and the equation and its statistical significance quantified by r^2 is given in the caption.
- The statistical significance is fairly low, though given the large uncertainties in the abundance estimations, this is not surprising.
- The equation and r^2 value is: [K/Fe]= −0.21×[Fe/H]+0.97, with r^2 =0.37.

### 2018-07-16 article/arxiv:mnras copy/arxivmnras.tex
arxiv/mnras subfolder+zip

% mnras_template.tex
%
% LaTeX template for creating an MNRAS paper
%
% v3.0 released 14 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaks to wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[a4paper,fleqn,usenatbib]{mnras}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

@@

\newcommand{\teff}{T_{\rm eff}}
\newcommand{\logg}{\log_{10}(g/{\rm cm\,s}^{-2})}
\let\ACMmaketitle=\maketitle
\renewcommand{\maketitle}{\begingroup\let\footnote=\thanks \ACMmaketitle\endgroup}
%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Mg--K stars in LAMOST]{On the discovery of K-enhanced and possibly Mg-depleted stars throughout the Milky Way\footnote{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[Kemp et al.]{Alex J. Kemp,$^{1}$\thanks{E-mail: ajkem1@student.monash.edu}
Andrew R. Casey,$^{1,2}$
Matthew T. Miles,$^{1}$
Brodie J. Norfolk,$^{1}$\newauthor
John C. Lattanzio,$^{1}$
Amanda I. Karakas,$^{1}$
Kevin C. Schlaufman,$^{3}$
Anna Y.~Q. Ho,$^{4}$\newauthor
Christopher A. Tout,$^{1,5}$
Melissa Ness,$^{6}$
Alexander P. Ji$^{7}$
\\
% List of institutions
$^{1}$School of Physics \& Astronomy, Monash University, Clayton 3800, Victoria, Australia\\
$^{2}$Faculty of Information Technology, Monash University, Clayton 3800, Victoria, Australia\\
$^{3}$Department of Physics and Astronomy, Johns Hopkins University, Baltimore, MD 21218, USA\\
$^{4}$Cahill Center for Astrophysics, California Institute of Technology, MC 249-17, 1200 E California Blvd, Pasadena, Ca, 91125, USA\\
$^{5}$Institute of Astronomy, Madingley Road, Cambridge, CB3 0HA, United Kingdom\\
$^{6}$Department of Astronomy, Columbia University, 550 West 120th Street New York, New York 10027\\
$^{7}$The Observatories of the Carnegie Institution of Washington, 813 Santa Barbara St., Pasadena, CA 91101, USA
}
% These dates will be filled out by the publisher
\date{Accepted 2018 XX XX. Received 2018 YY YY; in original form 2018 ZZ ZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2018}

@@

% Abstract of the paper
%The detailed chemical composition of a star acts as a fossil record of the conditions when it formed.

@@

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
methods: data analysis -- catalogues -- stars: chemically peculiar -- Galaxy: abundances -- Galaxy: evolution -- galaxies: globular clusters: individual: evolution
\end{keywords}

@@

%A targeted search for [K/Fe] in RGB and main sequence turn-off stars in other clusters 
A targeted search for [K/Fe] in other globular clusters (NGC 6752, NGC 6121, NGC 1904, NGC 104, NGC 6397, NGC 7099, and $\omega$ Centauri) and field stars concluded that all K abundance ratios fell within the bounds of the Mg-normal population in NGC 2419 \citep{carretta2013}, and no correlations between Mg and K were observed. Recent work by \cite{cerniauskas201747tuc} searched for unusual abundance patterns in Mg and K in NGC 104 by deriving abundances using 2dF/HERMES spectra, and a more comprehensive study involving over 400 stars in NGC 104, NGC 6752, and NGC 6809 by \cite{mucciarelli2017K} using FLAMES spectra \citep{cerniauskas201747tuc} both found no correlations between Mg and K, and no significant intrinsic spreads in either Mg or K.

@@

We fit a Gaussian profile of amplitude $A$ to the flux residuals for all three absorption lines in the Mg triplet (5167\,\AA, 5172\,\AA, 5184\,\AA) as well as the K doublet (7665\,\AA, 7699\,\AA) for all \LamostGiants\ giants. For each star we recorded the amplitudes, widths (standard deviations) and wavelength (mean) about which the Gaussian profiles were fit. The amplitude was used as the measure of the discrepancy from the model spectra, and is analogous to the depth of the absorption line, and in principle linearly dependent on the equivalent width. This measure was favoured as more reliable than attempting to quantify line widths from the low resolution \lamost\ spectra. %The relationship between equivalent width ($EW$), the amplitude ($A$) and the Gaussian width ($\sigma$) is given by $EW=\frac{2\pi A}{\sigma}$.

@@

It can be assumed that some stellar absorption is already accounted for by our data-driven model. In a sense, the data-driven model predicts a `typical' spectrum for a star with the given stellar parameters. This `typical` spectrum will include some contribution from all abundances (e.g., Mg, K, Al, Na), which is encapsulated by the overall metallicity [Fe/H]. That is to say that for a star of [Fe/H]$ = 0$, our data-driven model is predicting the spectrum of a \emph{typical} star at $[{\rm Fe/H}] = 0$, and that typical star would have $[{\rm K/Fe}] \sim 0$. We synthesise spectra to account for the flux residuals \emph{away} from the data-driven model. 
%@andy
% vt = 2.700 ? 0.509 log g km/s. (7

@@

%\todo{The presence of Na enhancements were visually estimated from the sample of 112 candidate stars' flux spectra. Flux-based estimates placed at most 40 of the 112 stars (35\%) as being likely Na enhanced targets.} Na abundances calculated from the \lamost\ spectra later revealed 30\% of the target stars with [Na/Fe] above 0.5\,dex. \todo{@andy add anything specific to Na abundance methods from LAMOST}.

@@

\begin{subfigure}{0.35\textwidth}
\centering
	\includegraphics[width=\columnwidth]{Navsradvel.png}
    \caption{[Na/Fe] vs radial velocity for the candidate stars.}
    \label{Navsradvel}
\end{subfigure}
%\end{figure*}
%\begin{figure*}
%\ContinuedFloat

@@

However, we concluded that the high [Na/Fe] abundance ratios we derive are likely due to interstellar dust contributing. Nearly every star with apparently enriched [Na/Fe] showed notably higher E(B-V) \citep{schlafly2011}, and all but four stars with high [Na/Fe] are found in the disk of our Galaxy, at low absolute galactic latitudes and velocities (Figures \ref{Navsb} and \ref{Navsradvel}). Thus, we find no evidence for genuine  enhancement of [Na/Fe] among our Mg--K candidates.
%suggesting that the stellar absorption lines are blended with interstellar dust absorption. This is supported by Figures \ref{Navsb} and \ref{Navsradvel}, which show the [Na/Fe] distribution with respect to galactic latitude and the radial velocity. 
%It is apparent that almost all of the stars in the anomalous group lie close to the disk of the galaxy, with radial velocities at least somewhat close to zero.
%However, further investigation revealed no evidence of a diffuse interstellar band (DIB) impacting LAMOST spectra around the Na doublet (nor around the Mg or K lines).

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{KvsMg.png}
    \caption{[K/Fe] vs [$\alpha$/Fe] for the candidate stars, overlaid with [K/Fe] vs [Mg/Fe] abundances for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015} as well as the three candidates observed using Magellan/MIKE (red diamonds). These three stars' abundances as per the \lamost\ spectra are indicated in the figure (red circles). Note that in principle, [$\alpha$/Fe] acts only as an upper limit for [Mg/Fe] and is used as such for our sample in this figure due to difficulties in calculating reliable [Mg/Fe] from \lamost\ data.}
    \label{KvsMg}
\end{figure}
 %See Section \ref{sec:method} for discussion on the use of [$\alpha$/Fe] as a proxy for [Mg/Fe].} 
\begin{figure}
	\includegraphics[width=\columnwidth]{KvsFe.png}
    \caption{[K/Fe] vs [Fe/H] for the candidate stars, overlaid with [K/Fe] vs [Fe/H] for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}. The linear regression formula is \textrm{[K/Fe]$=-0.21 \times$[Fe/H]$+0.97$, with r$^2$=0.37}.}
    \label{KvsFe}
\end{figure}

@@

%Significantly enhanced [K/Fe] is rare; significantly enhanced [K/Fe] without an accompanying depletion of [Mg/Fe] is unknown. The candidate stars are also spread across a wide range of metallicities.

@@

%Certainly the idea that both groups of anomalous stars arise from the same polluter source ought to be entertained.

%\todo{However, beyond the question of whether the [K/Fe]-[Fe/H] anti-correlation is real or not, the extreme difficulty of forming a cloud of Mg-depleted, K enriched material in the first place must be emphasized. Indeed, if we assume the primordial abundances (pre-mystery event) are similar to those of NGC 2419's Mg-normal population, then it is impossible. If the primordial cloud already has [Mg/Fe]$\approx 0.5$, to reduce this necessitates the addition of large amounts of iron rich material that is also very depleted in [Mg/Fe]. But as soon significant amounts of iron are added, [Fe/H] for the subsequent Mg-depleted population should increase, while no significant [Fe/H] variation between the two populations is observed \citep{cohenkirby2012, mucciarelli2012}. This implies that the mystery polluter star may have released its material into an environment enriched only by Big-Bang Nucleosynthesis (BBNS)}

%\todo{One major issue facing this explanation is that it requires a single gas cloud to form many generations of stars almost continuously in order to be consistent with Figure \ref{KvsFe}. This is only known to occur in inside true galaxies, which are massive enough to form multiple star forming regions. Allowing the candidate stars to have originated in a dwarf Galaxy which later merged with the Milky Way introduces many issues. The required mass to be polluted by the mystery object increases drastically, implying multiple pollution events. But invoking multiple pollution events means that the rarity of the signal is harder to explain: if it happened multiple times within a single dwarf Galaxy, why not in other places? Further, a merger should result in stars with highly elliptical orbits, while the candidates identified appear to be disk stars.}

%\todo{More generally, the [K/Fe]-[Fe/H] relation we observed is supportive of the origin of the Mg--K anti-correlation being temporally confined to an early epoch in the evolution of galaxies and globular clusters. However, this is not necessarily the only interpretation. For example, it could be that the K forming process is happening throughout the life of the Galaxy, but the amount of K produced decreases with the metallicity of the polluter star, though there is no obvious reason why this would be the case.}

%An intriguing anti-correlation between [K/Fe] and [Fe/H] is observed, although whether or not this relation is physical remains uncertain without further higher resolution observations of the candidates. Further high resolution observations will also allow Mg and other elemental abundances to be determined.

%Upon conducting an abundance analysis, anomalously high levels of K were found in the sample, with levels of [K/Fe] as high as 1.5 confirmed through high resolution spectroscopy using Magellan/MIKE. The [K/Fe] abundances were not consistent with the extreme populations previsously identified in either NGC 2419 or NGC 2808. No conclusion can be reached regarding the presence of [Mg/Fe] depletions in the sample as [Mg/Fe] abundances were unable to be determined from the \lamost\ spectra.

\section*{Acknowledgements}
We thank David W. Hogg (NYU), and Hans-Walter Rix (MPIA).
%- Magellan/MIKE and Australian government
ARC is supported through an Australian Research Council Discovery Project under grant DP160100637.
AYQH is supported by a Fulbright grant through the German-American Fulbright Commission and a National Science Foundation Graduate Research Fellowship under Grant No. DGE-1144469. 
CAT thanks Churchill College for his fellowship and Monash University for hosting him as a Kevin Westfold distinguished visitor.
This research has made use of NASA's Astrophysics Data System.
Guoshoujing Telescope (the Large Sky Area Multi-Object Fiber Spectroscopic Telescope LAMOST) is a National Major Scientific Project built by the Chinese Academy of Sciences. Funding for the project has been provided by the National Development and Reform Commission. LAMOST is operated and managed by the National Astronomical Observatories, Chinese Academy of Sciences.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

% The best way to enter references is to use BibTeX:

\bibliographystyle{mnras}
\bibliography{mgkbib} % if your bibtex file is called example.bib

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%

@@

\begin{table*}
\centering
\caption{Tabulated data for 10 of the 112 candidate stars. Data for the full sample is available online.}
\label{data:lamost}
\begin{tabular}{cccccccccccccc}
\hline
\textbf{2MASSID} & \textbf{RA} & \textbf{DEC} & \textbf{S/N} & \textbf{V$_\textrm{r}$} & \textbf{T$_\textrm{eff}$} & $\boldsymbol \log{ \, \textbf{g}}$ & \textbf{{[}Fe/H{]}} & \textbf{{[}$\alpha$/Fe{]}} & \textbf{$\boldsymbol \chi_r ^\textbf{2}$} & \textbf{{[}K/Fe{]}} & \textbf{Error} & \textbf{{[}Na/Fe{]}} & \textbf{Error} \\ 
- & {[}deg{]} & {[}deg{]} & [pixel$^{-1}]$ & {[${\rm km\,s}^{-1}$]} & {[}K{]} & $[{\rm cm\,s}^{-2}]$ & {[}dex{]} & {[}dex{]} & - & {[}dex{]} & {[}dex{]} & {[}dex{]} & {[}dex{]} \\ \hline
J000908.89+124821.9 & 2.2871 & 12.8061 & 10 & -78.55 & 4892 & 2.82 & -0.12 & 0.33 & 0.19 & 1.08 & 0.26 & 0.86 & 0.23 \\
J002619.36+565612.1 & 6.5807 & 56.9367 & 31 & -39.57 & 4205 & 1.49 & 0.22 & 0.06 & 0.76 & 0.62 & 0.22 & 0.39 & 0.22 \\
J002907.61+354701.0 & 7.2817 & 35.7836 & 15 & -82.74 & 5116 & 3.56 & 0.24 & 0.17 & 0.18 & 1.01 & 0.21 & -0.20 & 0.20 \\
J003451.10+424543.0 & 8.7130 & 42.7620 & 15 & -79.15 & 4460 & 2.10 & -0.56 & 0.24 & 0.31 & 0.96 & 0.33 & -0.16 & 0.20 \\
J005649.98+391722.9 & 14.2083 & 39.2897 & 41 & -46.77 & 4578 & 2.67 & 0.31 & 0.1 & 0.44 & 0.76 & 0.23 & -0.02 & 0.20 \\
J010305.95+043445.9 & 15.7748 & 4.5794 & 90 & 20.69 & 4646 & 2.72 & 0.1 & 0.05 & 1.17 & 0.95 & 0.21 & -0.07 & 0.20 \\
J011949.36+063411.4 & 19.9557 & 6.5699 & 479 & -28.18 & 4820 & 2.61 & -0.29 & 0.09 & 2.38 & 1.03 & 0.20 & -0.04 & 0.20 \\
J013039.08+404843.8 & 22.6628 & 40.8122 & 71 & -80.34 & 4355 & 2.01 & -0.09 & 0.14 & 0.93 & 0.92 & 0.21 & 0.46 & 0.21 \\
J030101.42+560042.3 & 45.2560 & 56.0118 & 88 & -39.27 & 4878 & 2.53 & -0.32 & 0.09 & 0.67 & 1 & 8.70 & -0.02 & 0.20 \\
J032423.46+425429.6 & 51.0978 & 42.9082 & 23 & -56.74 & 4649 & 2.63 & -0.11 & -0.01 & 0.34 & 1.12 & 0.22 & 0.80 & 0.20 \\ \hline
\end{tabular}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

% End of mnras_template.tex

>>>>

\documentclass[a4paper,fleqn,usenatbib]{mnras}

\usepackage{newtxtext,newtxmath}

\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

@@

\newcommand{\teff}{T_{\rm eff}}
\newcommand{\logg}{\log_{10}(g/{\rm cm\,s}^{-2})}
\let\ACMmaketitle=\maketitle
\renewcommand{\maketitle}{\begingroup\let\footnote=\thanks \ACMmaketitle\endgroup}

\title[Mg--K stars in LAMOST]{On the discovery of K-enhanced and possibly Mg-depleted stars throughout the Milky Way\footnote{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}}

\author[Kemp et al.]{Alex J. Kemp,$^{1}$\thanks{E-mail: ajkem1@student.monash.edu}
Andrew R. Casey,$^{1,2}$
Matthew T. Miles,$^{1}$
Brodie J. Norfolk,$^{1}$\newauthor
John C. Lattanzio,$^{1}$
Amanda I. Karakas,$^{1}$
Kevin C. Schlaufman,$^{3}$
Anna Y.~Q. Ho,$^{4}$\newauthor
Christopher A. Tout,$^{1,5}$
Melissa Ness,$^{6}$
Alexander P. Ji$^{7}$
\\
$^{1}$School of Physics \& Astronomy, Monash University, Clayton 3800, Victoria, Australia\\
$^{2}$Faculty of Information Technology, Monash University, Clayton 3800, Victoria, Australia\\
$^{3}$Department of Physics and Astronomy, Johns Hopkins University, Baltimore, MD 21218, USA\\
$^{4}$Cahill Center for Astrophysics, California Institute of Technology, MC 249-17, 1200 E California Blvd, Pasadena, Ca, 91125, USA\\
$^{5}$Institute of Astronomy, Madingley Road, Cambridge, CB3 0HA, United Kingdom\\
$^{6}$Department of Astronomy, Columbia University, 550 West 120th Street New York, New York 10027\\
$^{7}$The Observatories of the Carnegie Institution of Washington, 813 Santa Barbara St., Pasadena, CA 91101, USA
}

\date{Accepted 2018 XX XX. Received 2018 YY YY; in original form 2018 ZZ ZZ}

\pubyear{2018}

@@

@@

\begin{keywords}
methods: data analysis -- catalogues -- stars: chemically peculiar -- Galaxy: abundances -- Galaxy: evolution -- galaxies: globular clusters: individual: evolution
\end{keywords}

@@

A targeted search for [K/Fe] in other globular clusters (NGC 6752, NGC 6121, NGC 1904, NGC 104, NGC 6397, NGC 7099, and $\omega$ Centauri) and field stars concluded that all K abundance ratios fell within the bounds of the Mg-normal population in NGC 2419 \citep{carretta2013}, and no correlations between Mg and K were observed. Recent work by \cite{cerniauskas201747tuc} searched for unusual abundance patterns in Mg and K in NGC 104 by deriving abundances using 2dF/HERMES spectra, and a more comprehensive study involving over 400 stars in NGC 104, NGC 6752, and NGC 6809 by \cite{mucciarelli2017K} using FLAMES spectra \citep{cerniauskas201747tuc} both found no correlations between Mg and K, and no significant intrinsic spreads in either Mg or K.

@@

We fit a Gaussian profile of amplitude $A$ to the flux residuals for all three absorption lines in the Mg triplet (5167\,\AA, 5172\,\AA, 5184\,\AA) as well as the K doublet (7665\,\AA, 7699\,\AA) for all \LamostGiants\ giants. For each star we recorded the amplitudes, widths (standard deviations) and wavelength (mean) about which the Gaussian profiles were fit. The amplitude was used as the measure of the discrepancy from the model spectra, and is analogous to the depth of the absorption line, and in principle linearly dependent on the equivalent width. This measure was favoured as more reliable than attempting to quantify line widths from the low resolution \lamost\ spectra.

@@

It can be assumed that some stellar absorption is already accounted for by our data-driven model. In a sense, the data-driven model predicts a `typical' spectrum for a star with the given stellar parameters. This `typical` spectrum will include some contribution from all abundances (e.g., Mg, K, Al, Na), which is encapsulated by the overall metallicity [Fe/H]. That is to say that for a star of [Fe/H]$ = 0$, our data-driven model is predicting the spectrum of a \emph{typical} star at $[{\rm Fe/H}] = 0$, and that typical star would have $[{\rm K/Fe}] \sim 0$. We synthesise spectra to account for the flux residuals \emph{away} from the data-driven model.

@@

@@

\begin{subfigure}{0.35\textwidth}
\centering
	\includegraphics[width=\columnwidth]{Navsradvel.png}
    \caption{[Na/Fe] vs radial velocity for the candidate stars.}
    \label{Navsradvel}
\end{subfigure}

@@

However, we concluded that the high [Na/Fe] abundance ratios we derive are likely due to interstellar dust contributing. Nearly every star with apparently enriched [Na/Fe] showed notably higher E(B-V) \citep{schlafly2011}, and all but four stars with high [Na/Fe] are found in the disk of our Galaxy, at low absolute galactic latitudes and velocities (Figures \ref{Navsb} and \ref{Navsradvel}). Thus, we find no evidence for genuine  enhancement of [Na/Fe] among our Mg--K candidates.

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{KvsMg.png}
    \caption{[K/Fe] vs [$\alpha$/Fe] for the candidate stars, overlaid with [K/Fe] vs [Mg/Fe] abundances for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015} as well as the three candidates observed using Magellan/MIKE (red diamonds). These three stars' abundances as per the \lamost\ spectra are indicated in the figure (red circles). Note that in principle, [$\alpha$/Fe] acts only as an upper limit for [Mg/Fe] and is used as such for our sample in this figure due to difficulties in calculating reliable [Mg/Fe] from \lamost\ data.}
    \label{KvsMg}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{KvsFe.png}
    \caption{[K/Fe] vs [Fe/H] for the candidate stars, overlaid with [K/Fe] vs [Fe/H] for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}. The linear regression formula is \textrm{[K/Fe]$=-0.21 \times$[Fe/H]$+0.97$, with r$^2$=0.37}.}
    \label{KvsFe}
\end{figure}

@@

@@

\section*{Acknowledgements}
We thank David W. Hogg (NYU), and Hans-Walter Rix (MPIA).
ARC is supported through an Australian Research Council Discovery Project under grant DP160100637.
AYQH is supported by a Fulbright grant through the German-American Fulbright Commission and a National Science Foundation Graduate Research Fellowship under Grant No. DGE-1144469. 
CAT thanks Churchill College for his fellowship and Monash University for hosting him as a Kevin Westfold distinguished visitor.
This research has made use of NASA's Astrophysics Data System.
Guoshoujing Telescope (the Large Sky Area Multi-Object Fiber Spectroscopic Telescope LAMOST) is a National Major Scientific Project built by the Chinese Academy of Sciences. Funding for the project has been provided by the National Development and Reform Commission. LAMOST is operated and managed by the National Astronomical Observatories, Chinese Academy of Sciences.

\bibliographystyle{mnras}
\bibliography{mgkbib}

@@

\begin{table*}
\centering
\caption{Tabulated data for 10 of the 112 candidate stars. Data for the full sample is available online.}
\label{data:lamost}
\begin{tabular}{cccccccccccccc}
\hline
\textbf{2MASSID} & \textbf{RA} & \textbf{DEC} & \textbf{S/N} & \textbf{V$_\textrm{r}$} & \textbf{T$_\textrm{eff}$} & $\boldsymbol \log{ \, \textbf{g}}$ & \textbf{{[}Fe/H{]}} & \textbf{{[}$\alpha$/Fe{]}} & \textbf{$\boldsymbol \chi_r ^\textbf{2}$} & \textbf{{[}K/Fe{]}} & \textbf{Error} & \textbf{{[}Na/Fe{]}} & \textbf{Error} \\ 
- & {[}deg{]} & {[}deg{]} & [pixel$^{-1}]$ & {[${\rm km\,s}^{-1}$]} & {[}K{]} & $[{\rm cm\,s}^{-2}]$ & {[}dex{]} & {[}dex{]} & - & {[}dex{]} & {[}dex{]} & {[}dex{]} & {[}dex{]} \\ \hline
J000908.89+124821.9 & 2.2871 & 12.8061 & 10 & -78.55 & 4892 & 2.82 & -0.12 & 0.33 & 0.19 & 1.08 & 0.26 & 0.86 & 0.23 \\
J002619.36+565612.1 & 6.5807 & 56.9367 & 31 & -39.57 & 4205 & 1.49 & 0.22 & 0.06 & 0.76 & 0.62 & 0.22 & 0.39 & 0.22 \\
J002907.61+354701.0 & 7.2817 & 35.7836 & 15 & -82.74 & 5116 & 3.56 & 0.24 & 0.17 & 0.18 & 1.01 & 0.21 & -0.20 & 0.20 \\
J003451.10+424543.0 & 8.7130 & 42.7620 & 15 & -79.15 & 4460 & 2.10 & -0.56 & 0.24 & 0.31 & 0.96 & 0.33 & -0.16 & 0.20 \\
J005649.98+391722.9 & 14.2083 & 39.2897 & 41 & -46.77 & 4578 & 2.67 & 0.31 & 0.1 & 0.44 & 0.76 & 0.23 & -0.02 & 0.20 \\
J010305.95+043445.9 & 15.7748 & 4.5794 & 90 & 20.69 & 4646 & 2.72 & 0.1 & 0.05 & 1.17 & 0.95 & 0.21 & -0.07 & 0.20 \\
J011949.36+063411.4 & 19.9557 & 6.5699 & 479 & -28.18 & 4820 & 2.61 & -0.29 & 0.09 & 2.38 & 1.03 & 0.20 & -0.04 & 0.20 \\
J013039.08+404843.8 & 22.6628 & 40.8122 & 71 & -80.34 & 4355 & 2.01 & -0.09 & 0.14 & 0.93 & 0.92 & 0.21 & 0.46 & 0.21 \\
J030101.42+560042.3 & 45.2560 & 56.0118 & 88 & -39.27 & 4878 & 2.53 & -0.32 & 0.09 & 0.67 & 1 & 8.70 & -0.02 & 0.20 \\
J032423.46+425429.6 & 51.0978 & 42.9082 & 23 & -56.74 & 4649 & 2.63 & -0.11 & -0.01 & 0.34 & 1.12 & 0.22 & 0.80 & 0.20 \\ \hline
\end{tabular}
\end{table*}

\bsp	
\label{lastpage}
\end{document}
